Holomorphic field theories and higher algebra

### 2023-01-27 draft.tex
merge

Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
If $V$ is a holomorphic dg Lie algebra, 
then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms.

@@

In traditional physics there are a few basic types of field theories, 
and they can be assembled into combinations in natural ways,
of which the Standard Model offers a nice example.
The basic types are\footnote{For the experts, we remark that we focus above on the core field content, and ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
\begin{itemize}
\item {\em Scalar} field theories where the fields are maps from $M$ to a vector space $V$, or natural generalizations like taking sections of a vector bundle $V \to M$. The Higgs boson appears as part of a scalar field theory.
\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space or, typically, a section of a spinor bundle. Such theories are often used to describe matter, such as electron fields.
\item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
\item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
\end{itemize}
The Standard Model involves the first three types,
and the different fields interact in intricate ways.

@@

The most elementary holomorphic field theory is a generalization of the so-called `$\beta\gamma$ system' which is primarily studied in the context of string theory.
The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on $X$.
The fields of the theory consist of pairs 
\begin{align*}
\gamma & \in \Gamma(X,V)\\
\beta & \in \Omega^{n,n-1}(X,V^*) .
\end{align*}
The action functional is 
\beqn
\int_X \beta \wedge \dbar \gamma 
\eeqn
which utilizes the natural pairing between $V$ and $V^*$. 
The theory is free, just like the ordinary $\beta\gamma$ system on Riemann surfaces.

Notice that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
\beqn
\beta \mapsto \beta + \dbar \eta , \quad \eta \in \Omega^{n,n-2}(X,V^*)
\eeqn
For this model to be well-posed at the quantum level we must include the ghosts $\eta$.
Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..

@@

The precise space of fields, in cohomological degree zero, consist of pairs $(\gamma, \beta)$ where $\gamma \colon X \to Y$ is a smooth map and 
\[
\beta \in \Omega^{n,n-1}(X, f^* \T^*_Y) 
\]
where $\T^*_Y$ is the holomorphic cotangent bundle of $Y$. 
The action functional is the familiar one
\beqn
\int_X \beta \dbar \gamma .
\eeqn

\subsubsection{Holomorphic gravity}

Perturbatively, any model of gravity describes, in part, deformations of the moduli space of metric structures on a given manifold. 
There is a holomorphic avatar of this which describes deformations of complex structure.
The fields consist of pairs $(\mu, \eta)$ where
\begin{align*}
\mu & \in \Omega^{0,1}(X, \T_X) \\
\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
\end{align*}
The action functional is
\beqn
\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
\eeqn
where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.

In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure where we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
Kodaira--Spencer theory is the holomorphic theory whose fields consist of $(0,1)$ forms on $X$ with values in the holomorphic tangent bundle $\T_X$
\beqn
\mu \in \Omega^{0,1}(X,\T_X) .
\eeqn 
A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
The action functional is very similar to the Chern--Simons action
\beqn
S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
\eeqn
The integrand is not defined globally.
In the integral we use the Calabi--Yau form to identify the integrand with 
\brian{finish}

\subsection{Local version and examples from supersymmetric field theories}

@@

By a {\em supercharge}, one means an odd supertranslation $\cQ \in \ft$, and
a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
The classification of all twists is a completely algebraic question,
and we refer to~\autocite{ESsusy} for a complete classification of all twists \owen{of SYM?} in dimensions from $1$ to~$10$.

@@

We now turn to quantization, and our phase space will be, for simplicity, the algebraic loop space $V[z,z^{-1}]$ of a symplectic complex vector space $V$.
Following the case of mechanics, we might ask for a deformation of the Poisson algebra
\beqn
\cO\left( V((z)) \right) .
\eeqn
Like the symplectic form on $V((z))$, the Poisson bracket is given in terms of the residue pairing.
%into an associative algebra.
%A subtlety here is that $\cO(V[z,z^{-1}])$ does not possess a Poisson bracket, 
%due to the  infinite-dimensionality of $V[z,z^{-1}]$.
%The naive formulas from functions on a finite-dimensional symplectic vector space only make sense on a subset of observables here.
%One workaround is to replace $V[z,z^{-1}]$ with $V((z))$, the $V$-valued Laurent series,
%which we view as ``formal loops in $V$.''
%There is manifestly an inclusion $V[z,z^{-1}] \hookrightarrow V((z))$ and hence an algebra map $\cO(V((z))) \to \cO(V[z,z^{-1}])$
%where 
%\[
%\cO(V((z))) = \Sym(V^* [z,z^{-1}]).
%\]
%On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\omega^* \otimes \Res$ on $V^* [z,z^{-1}]$.
%Hence for $\cO(V((z)))$, we can ask for a deformation quantization,
%and there is a nice answer: 
The standard Heisenberg commutation relations determine a Weyl algebra $W[V]$ for this formal loop space.
As a vector space $W[V]$ is isomorphic to $\cO(V((z)))$, 
just as the simplest Weyl algebra is isomorphic to $\cO(V)$ as a vector space,
but the product structure is modified by quantization.
We expect, by analogy with the simplest case, that any quantization of a bigger algebra (e.g., for observables of the holomorphic loop space) contains this quantization as its algebraic skeleton.

@@

It is a remarkable fact, suggested by physicists, that there is also a map
\[
Y \colon {\rm Vac}[V] \to \End({\rm Vac}[V])[[z, z^{-1}]],
\]
known as the {\em vertex operator} or {\em state-field correspondence},
which is closely related to the $W[V]$-action.
The intuition behind $Y$ is that for any map $\phi: \CC^\times \to V$ and for any point $w \in \CC^\times$, 
there is a restriction of $\phi$ to a little disc around $w$.
That is, there is a restriction map $r_w: V[z,z^{-1}] \to V[[t]]$, where $t$ is the local coordinate $t = z-w$.
Hence there is a $w$-dependent map $\cO(V[[t]]) \to \cO(V[z,z^{-1}])$ by pulling back a function along $r_w$;
this map determines a $w$-dependent action of $\cO(V[[t]])$ on $\cO(V[[z]])$.
One can, in essence, quantize this map, by trying to extend the formulas of the $W[V]$-action,
and this leads to the map~$Y$.
If one axiomatizes the behavior of $Y$, one is led to the notion of a vertex algebra.

@@

We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of `compactification'. 
It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
Then, compactification involves integrating out the remaining circle direction.
Concretely, any smooth function on $\CC^\times$ can be decomposed in polar coordinates as
\[
\phi(r,\theta) = \sum_{k \in \ZZ} \phi_k(r) e^{2 \pi i k \theta} ,
\]
where $\phi_k(r)$ is a smooth function depending only on the radius $r \in \RR_+$.
Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
We interpret $\sum_{k \in \ZZ} \phi_k(t)$ as smooth map from $\RR$ to the formal (free) loop space $LV = V[z,z^{-1}]$.

@@

\subsection{Algebras in higher dimensions }

@@

It is important to have an explicit dg commutative algebra that models the derived global sections for functions on punctured formal disk,
and not just the cohomology groups.
There is a beautiful, explicit dg model $\sfA^\bu_d$ for the formal version derived global sections due to Faonte-Hennion-Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities. 
While we won't go into details about this model, we remark on a few important points all of which we take from \cite{FHK}:
\begin{itemize}
\item The complex $\sfA^\bu_d$ is concentrated in degrees $0,\ldots,d-1$ and its cohomology is the same as the cohomology of $\RR \Gamma(\mathring{\DD}^d, \cO)$ described above.
\item There is a polynomial version $\sfA_{d,poly}^\bu$ and explicit embeddings of commutative dg algebras 
\beqn
\sfA_{d}^\bu \hookleftarrow \sfA_{d,poly}^\bu \hookrightarrow \Omega^{0,\bu}(\CC^d - 0) .
\eeqn
The left embedding replaces the inclusion of Laurent polynomials into Laurent series.
The right embedding replaces the inclusion of Laurent polynomials into the Dolbeault complex on $\CC^\times$.
\item There is a higher residue map $\text{Res} \colon \sfA_d^{\bu} \to \CC[-d+1]$ which is compatible with integration over the $2d-1$ sphere
\beqn
\label{eq:res}
\Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d^d z,
\eeqn
under the above embeddings.
Here $\d^d z = \d z_1 \wedge \cdots \wedge \d z_d$ is the standard holomorphic volume form.
\end{itemize}

@@

\begin{dfn}[\cite{FHK}]
For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$\fg \otimes \sfA_d$.
We denote it by~$\fg^\bullet_d$.
\end{dfn}

There are natural central extensions of this sphere algebra as {\em $L_\infty$ algebras},
parallel to the affine Lie algebras appearing as central extensions of the loop algebra.
An $L_\infty$ algebra is a generalization of a Lie algebra;
it is graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k \colon L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi condition for a standard Lie algebra.
For an overview (and an actual definition!) we recommend \owen{add citations}.

In our setting of $\fg^\bullet_d$, Faonte-Hennion-Kapranov introduced central extensions of the sphere algebra that only affect the $d$-bracket.
For any $\fg$-invariant degree $d+1$ polynomial $\theta \in \Sym^{d+1}(\fg^*)^\fg$, the cocycle which defines the $L_\infty$ central extension is
\[
\label{fhk cocycle}
\begin{array}{cccc}
\theta_{\rm FHK} : & (\sfA_d \tensor \fg)^{\tensor (d+1)} & \to & \CC\\ 
& a_0 \otimes \cdots \otimes a_d & \mapsto & \Res \left(\theta(a_0,\partial a_1,\ldots,\partial a_d)\right)
\end{array}.
\]
This cocycle has total cohomological degree $+2$ as an element in the Lie algebra cohomology of $\fg^\bu_{d}$ and so determines a central extension of $L_\infty$ algebras
\[
\CC c \to \widetilde{\fg}^\bullet_{d, \theta} \to \fg^\bullet_d ,
\]
so that the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
They dubbed these the {\em higher Kac-Moody algebras}, 
as they specialize to the affine Lie algebras when~$d =1$.

These $L_\infty$ algebras are not just introduced on a whim.
In \cite{FHK} they are shown to appear naturally in various contexts,
notably in studying the derived moduli of $G$-bundles on a complex varieties of dimension~$d$.

@@

Observables, however, are supposed to live in vector spaces or dg vector spaces,
so we need to explain how to get algebras in that setting.
Thankfully, it is straightforward to get a linear version of this operad a dg operad (i.e., operad with values in dg vector spaces and using the tensor product as the symmetric monoidal product).
One simply takes the singular chain complex on each space of operations:
for each natural number $n$, take $C_*(\Disc_d(n); \CC)$ and take the induced chain map 
\[
C_*(\circ_i): C_*(\Disc_d(n); \CC) \otimes C_*(\Disc_d(m); \CC) \to C_*(\Disc_d(n+m-1); \CC)
\]
to produce a dg operad we denote~$C_*(\Disc_d)$.
(Note that as we always want to work with cochain complexes, we regrade the usual singular chains $C_*(X, \CC)$ to sit in nonpositive cohomological degrees. 
Likewise the composition $C_*(\circ_i)$ is then a cochain map.)

\begin{dfn}
An {\em algebra over the little $d$-discs operad} (or little $d$-discs algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_*(\Disc_d)$.
\end{dfn}

@@

We are again thinking about configuration spaces --- here of polydiscs inside larger polydiscs --- but we are remembering the complex structure explicitly.
To describe observables, we want to produce a dg colored operad that encodes the holomorphic nature of this situation.
We do {\em not} want to take singular chains, which would only remember the homotopy type;
instead, we choose to take the Dolbeault complex of each configuration space.
Note, however, that taking the Dolbeault complex is a contravariant functor,
so we get a {\em co}\/operad rather than an operad.
This notion bears the same relationship to operad as a coalgebra does to an algebra;
one simply reverses all the arrows and asks for an appropriate variant of the relations.
For instance, there is a composition
\begin{align}
\label{pdcirc}
\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, &\ldots, s_m, r_{i+1}, \ldots, r_n| R)) \to \\
&\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
\end{align}
\owen{I don't know how to eliminate the two numbers}
when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
(Composition is not defined if the radii do not match.)

An important technical point arises here: 
we need to be careful about functional analysis.
The wedge product map
\[
\Omega^{0,*}(X) \otimes \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
\]
is not a quasi-isomorphism in general (unlike with de Rham complexes),
but the completed projective tensor product as topological vector spaces 
\[
\Omega^{0,*}(X) \widehat{\otimes}_\pi \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
\]
is an isomorphism.
(We use here the standard Fr\'echet topology on smooth functions, extended to sections of vector bundles.)
Hence we should work in some category of cochain complexes of well-behaved topological vector spaces, such as convenient vector spaces, or something related.
This requirement makes sense when geometry matters (e.g., using the Dolbeault complex) and not just topology.
For an extensive discussion of these issues, see the appendices of~\cite{CG1}.
From hereon we will ignore function-analytic aspects and write $\otimes$,
with an appropriate symmetric monoidal category left implicit.

>>>>

Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
If $V$ is a holomorphic dg Lie algebra, 
then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on $X$.

@@

In traditional physics there are a few basic types of field theories, 
and they can be assembled into combinations in natural ways,
of which the Standard Model offers a nice example.
The basic types are\footnote{For the experts, we remark that we focus above on the core field content, and ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
\begin{itemize}
\item {\em Scalar} field theories where the fields are maps from $M$ to a vector space $V$, or natural generalizations like taking sections of a vector bundle $V \to M$. The Higgs boson appears as part of a scalar field theory.
\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space or, typically, a section of a spinor bundle. Such theories are often used to describe matter, such as electron fields.
\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
\item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
\item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
\end{itemize}
The Standard Model involves the first three types,
and the different fields interact in intricate ways.

@@

A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
When $\Sigma$ is a surface this theory can be written in such a way that makes its complex structure apparent.
First, we complexify the field $\phi$ which we can view as a pair of fields $\gamma, \Bar{\gamma}$.
When we do this, we can split it up into its chiral and anti-chiral `sectors'.
By chiral (anti-chiral) we mean part involving $\gamma$ ($\Bar{\gamma}$).
The holomorphic part is described by the following action
\beqn
\int_\Sigma \beta \wedge \dbar \gamma
\eeqn
where $\beta$ is a $(1,0)$ form on $\Sigma$ and should be thought of as a Lagrange multiplier for the field $\del \Bar{\gamma}$ which we now think about as having its own degrees of freedom (this is called the first-order formalism).
There is also a coupling between the chiral and anti-chiral sectors, 
for more details we refer to \cite{Kapustin,GGW}. 
This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta-\gamma$-\textit{system}.
It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.

There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta-\gamma$ system'.
The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
Above we took this bundle to be trivial.
The fields of the theory consist of pairs 
\begin{align*}
\gamma & \in \Gamma(X,V)\\
\beta & \in \Omega^{n,n-1}(X,V^*) .
\end{align*}
The action functional is identical $\int_X \beta \wedge \dbar \gamma$.

Notice that when $n = \dim_\C X > 1$ that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
\beqn
\beta \mapsto \beta + \dbar \eta , \quad \eta \in \Omega^{n,n-2}(X,V^*)
\eeqn
For this model to be well-posed at the quantum level we must include the ghosts $\eta$.
Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
This is one of the key differences between the ordinary $\beta-\gamma$ system and its higher dimensional version.
Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.

@@

The precise space of fields, in cohomological degree zero, consist of pairs $(\gamma, \beta)$ where $\gamma \colon X \to Y$ is a smooth map and 
\[
\beta \in \Omega^{n,n-1}(X, f^* \T^*_Y) 
\]
where $\T^*_Y$ is the holomorphic cotangent bundle of $Y$. 
The action functional is the familiar one
\beqn
\int_X \beta \dbar \gamma .
\eeqn 
Solutions to the equations of motion describe, in part, holomorphic maps $X \to Y$, but there is also derived information contained in this model.

\subsubsection{Holomorphic ``gravity''}

Perturbatively, any model of gravity describes, in part, deformations of the moduli space of metric structures on a given manifold. 
There is a holomorphic avatar of this which describes deformations of complex structure which has first appeared in the literature in work related to topological string theory on Calabi--Yau threefolds~\cite{BCOV}.
Because of its relationship to complex structures, the theory is referred to as \textit{Kodaira--Spencer theory}.
It has been mathematically championed in the works of Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; here we focus just on the more familiar three-dimensional version.
%The fields consist of pairs $(\mu, \eta)$ where
%\begin{align*}
%\mu & \in \Omega^{0,1}(X, \T_X) \\
%\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
%\end{align*}
%The action functional is
%\beqn
%\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
%\eeqn
%where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira spencer theory is a $(0,1)$ form on $X$ with values in the holomorphic tangent bundle $\T_X$
\beqn
\mu \in \Omega^{0,1}(X,\T_X) .
\eeqn 
A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
The action functional is very similar to the Chern--Simons action
\beqn
S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
\eeqn
In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
Forgoing the apparent global issues, we can still apply formal variational calculus to the action to obtain the equation of motion
\beqn
\dbar \mu + \frac12 [\mu,\mu] = 0 ,
\eeqn
where $[-,-]$ is the Schouten--Nijenhuis bracket (which reduces to just the natural bracket when restricted to vector fields).
The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
\subsection{Local version and examples from supersymmetric field theories}

@@

By a {\em supercharge}, one means an odd supertranslation $\cQ \in \ft$, and
a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
The classification of twisting supercharges is a completely algebraic question,
and we refer to~\autocite{ESsusy} for a complete classification for supersymmetry algebras in dimensions from $1$ to~$10$.

@@

We now turn to quantization, and our phase space will be, for simplicity, the formal loop space $V((z))$ of a symplectic complex vector space $V$.
Following the case of mechanics, we might ask for a deformation of the Poisson algebra
\beqn
\cO\left( V((z)) \right) .
\eeqn
Like the symplectic form on $V((z))$, the Poisson bracket is given in terms of the residue pairing.
%into an associative algebra.
%A subtlety here is that $\cO(V[z,z^{-1}])$ does not possess a Poisson bracket, 
%due to the  infinite-dimensionality of $V[z,z^{-1}]$.
%The naive formulas from functions on a finite-dimensional symplectic vector space only make sense on a subset of observables here.
%One workaround is to replace $V[z,z^{-1}]$ with $V((z))$, the $V$-valued Laurent series,
%which we view as ``formal loops in $V$.''
%There is manifestly an inclusion $V[z,z^{-1}] \hookrightarrow V((z))$ and hence an algebra map $\cO(V((z))) \to \cO(V[z,z^{-1}])$
%where 
%\[
%\cO(V((z))) = \Sym(V^* [z,z^{-1}]).
%\]
%On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\Omega^\bu \otimes \Res$ on $V^* [z,z^{-1}]$.
%Hence for $\cO(V((z)))$, we can ask for a deformation quantization,
%and there is a nice answer: 
The standard Heisenberg commutation relations determine a Weyl algebra $W[V]$ for this formal loop space.
As a vector space $W[V]$ is isomorphic to $\cO(V((z)))$, 
just as the simplest Weyl algebra is isomorphic to $\cO(V)$ as a vector space,
but the product structure is modified by quantization.
We expect, by analogy with the simplest case, that any quantization of a bigger algebra (e.g., for observables of the holomorphic loop space) contains this quantization as its algebraic skeleton.

@@

It is a remarkable fact, suggested by physicists, that there is also a map
\[
Y \colon {\rm Vac}[V] \to \End({\rm Vac}[V])[[z, z^{-1}]],
\]
known as the {\em vertex operator} or {\em state-field correspondence},
which is closely related to the $W[V]$-action.
The intuition behind $Y$ is that for any map $\phi: \CC^\times \to V$ and for any point $w \in \CC^\times$, 
there is a restriction of $\phi$ to a little disc around $w$.
That is, there is a restriction map $r_w: V((z)) \to V[[t]]$, where $t$ is the local coordinate $t = z-w$.
Hence there is a $w$-dependent map $\cO(V[[t]]) \to \cO(V((z)))$ by pulling back a function along $r_w$;
this map determines a $w$-dependent action of $\cO(V[[t]])$ on $\cO(V[[z]])$.
One can, in essence, quantize this map, by trying to extend the formulas of the $W[V]$-action,
and this leads to the map~$Y$.
If one axiomatizes the behavior of $Y$, one is led to the notion of a vertex algebra.

@@

We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of `compactification'. 
It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
Then, compactification involves integrating out the remaining circle direction.
Concretely, any smooth function on $\CC^\times$ can be decomposed in polar coordinates as
\[
\phi(r,\theta) = \sum_{k \in \ZZ} \phi_k(r) e^{2 \pi i k \theta} ,
\]
where $\phi_k(r)$ is a smooth function depending only on the radius $r \in \RR_+$.
Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
We interpret $\sum_{k \in \ZZ} \phi_k(r)$ as smooth map from $\RR$ to the formal loop space $LV$.

@@

\subsection{Algebras in higher dimensions }
\label{s:alghigh}

@@

It is important to have an explicit dg commutative algebra that models the derived global sections for functions on punctured formal disk,
and not just the cohomology groups.
There is a beautiful, explicit dg model $\sfA^\bu_d$ for the formal version derived global sections due to Faonte, Hennion, and Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities. 
While we won't go into details about this model, we remark on a few important points all of which we take from \cite{FHK}:
\begin{itemize}
\item The complex $\sfA^\bu_d$ is concentrated in degrees $0,\ldots,d-1$ and its cohomology is the same as the cohomology of $\RR \Gamma(\mathring{\DD}^d, \cO)$ described above.
\item There is a polynomial version $\sfA_{d,poly}^\bu$ and explicit embeddings of commutative dg algebras 
\beqn
\sfA_{d}^\bu \hookleftarrow \sfA_{d,poly}^\bu \hookrightarrow \Omega^{0,\bu}(\CC^d - 0) .
\eeqn
The left embedding replaces the inclusion of Laurent polynomials into Laurent series.
The right embedding replaces the inclusion of Laurent polynomials into the Dolbeault complex on $\CC^\times$.
\item There is a higher residue map $\text{Res} \colon \sfA_d^{\bu} \to \CC[-d+1]$ which is compatible with integration over the $2d-1$ sphere
\beqn
\label{eq:res}
\Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d^d z,
\eeqn
under the above embeddings.
Here $\d^d z = \d z_1 \wedge \cdots \wedge \d z_d$ is the standard holomorphic volume form.
\end{itemize}

@@

\begin{dfn}[\cite{FHK}]
\label{dfn:sphere}
For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$\fg \otimes \sfA_d$.
We denote it by~$\fg^\bullet_d$.
\end{dfn}

There are natural central extensions of this sphere algebra 
%as {\em $L_\infty$ algebras},
parallel to the affine Lie algebras appearing as central extensions of the loop algebra.
They are given by the data of a $\fg$-invariant degree $d+1$ polynomial $\theta \in \Sym^{d+1}(\fg^*)^G$.
The cocycle which defines the $L_\infty$ central extension is
\[
\label{fhk cocycle}
\begin{array}{cccc}
\theta_{\rm FHK} : & (\sfA_d \tensor \fg)^{\tensor (d+1)} & \to & \CC\\ 
& a_0 \otimes \cdots \otimes a_d & \mapsto & \Res \left(\theta(a_0,\partial a_1,\ldots,\partial a_d)\right)
\end{array}.
\]
This cocycle has total cohomological degree $+2$ as an element in the Lie algebra cohomology of $\fg^\bu_{d}$ and so determines a central extension of dg Lie algebras
\[
\CC c \to \Hat{\fg}^\bullet_{d, \theta} \to \fg^\bullet_d .
\]
There is a particularly nice model for this dg Lie algebra as an $L_\infty$ \textit{algebra} that we use in \cite{GWkm}.
An $L_\infty$ algebra is a generalization of a dg Lie algebra;
it is a graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k \colon L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi identity.
For an overview (and an actual definition!) we recommend \owen{add citations}.
In our setting the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
%They dubbed these the {\em higher Kac-Moody algebras}, 
%as they specialize to the affine Lie algebras when~$d =1$.

The algebras $\Hat{\fg}^\bullet_{d, \theta}$ are not just introduced on a whim.
In \cite{FHK} they are shown to appear naturally in various contexts,
notably in studying the derived moduli of $G$-bundles on a complex varieties of dimension~$d$.

@@

Observables, however, are supposed to live in vector spaces or dg vector spaces,
so we need to explain how to get algebras in that setting.
Thankfully, it is straightforward to get a linear version of this operad a dg operad (i.e., operad with values in dg vector spaces and using the tensor product as the symmetric monoidal product).
One simply takes the singular chain complex on each space of operations:
for each natural number $n$, take $C_\bu(\Disc_d(n); \CC)$ and take the induced chain map 
\[
C_\bu(\circ_i): C_\bu(\Disc_d(n); \CC) \otimes C_\bu(\Disc_d(m); \CC) \to C_\bu(\Disc_d(n+m-1); \CC)
\]
to produce a dg operad we denote~$C_\bu(\Disc_d)$.
(Note that as we always want to work with cochain complexes, we regrade the usual singular chains $C_\bu(X, \CC)$ to sit in nonpositive cohomological degrees. 
Likewise the composition $C_\bu(\circ_i)$ is then a cochain map.)

\begin{dfn}
An {\em algebra over the little $d$-discs operad} (or little $d$-discs algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_\bu(\Disc_d)$.
\end{dfn}

@@

We are again thinking about configuration spaces --- here of polydiscs inside larger polydiscs --- but we are remembering the complex structure explicitly.
To describe observables, we want to produce a dg colored operad that encodes the holomorphic nature of this situation.
We do {\em not} want to take singular chains, which would only remember the homotopy type;
instead, we choose to take the Dolbeault complex of each configuration space.
Note, however, that taking the Dolbeault complex is a contravariant functor,
so we get a {\em co}\/operad rather than an operad.
This notion bears the same relationship to operad as a coalgebra does to an algebra;
one simply reverses all the arrows and asks for an appropriate variant of the relations.
For instance, there is a composition
\begin{multline}
\label{pdcirc}
\circ_i: \Omega^{0,\bu}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R)) \to \\
\Omega^{0,\bu}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,\bu}(\PDisc_d(s_1, \ldots, s_m| S))
\end{multline}
\owen{I don't know how to eliminate the two numbers}
\brian{I like using multline instead of align}
when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
(Composition is not defined if the radii do not match.)

An important technical point arises here: 
we need to be careful about functional analysis.
The wedge product map
\[
\Omega^{0,\bu}(X) \otimes \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
\]
is not a quasi-isomorphism in general (unlike with de Rham complexes),
but the completed projective tensor product as topological vector spaces 
\[
\Omega^{0,\bu}(X) \widehat{\otimes}_\pi \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
\]
is an isomorphism.
(We use here the standard Fr\'echet topology on smooth functions, extended to sections of vector bundles.)
Hence we should work in some category of cochain complexes of well-behaved topological vector spaces, such as convenient vector spaces, or something related.
This requirement makes sense when geometry matters (e.g., using the Dolbeault complex) and not just topology.
For an extensive discussion of these issues, see the appendices of~\cite{CG1}.
From hereon we will ignore function-analytic aspects and write $\otimes$,
with an appropriate symmetric monoidal category left implicit.
